SuperScreen: An open-source package for simulating the magnetic response of two-dimensional superconducting devices

### 2022-03-16 main.tex
Add date accessed to online references

\title{\texttt{SuperScreen}: An open-source package for simulating the magnetic response of two-dimensional superconducting devices}

@@

This introduction to \SuperScreen is organized as follows: In Section~\ref{section:model} we outline the model and its assumptions, and in Section~\ref{section:implementation} we describe its numerical implementation. In Section~\ref{section:overview} we provide an overview of the structure of the \SuperScreen package and discuss some important development details. In Section~\ref{section:examples} we demonstrate how to perform several types of simulations using \SuperScreen and compare the results to analytical solutions and experimental results. Finally, in Section~\ref{section:conlusion} we conclude by discussing applications, limitations, and possible extensions of the package. Python scripts and Jupyter notebooks used to generate all figures presented below can be found in the GitHub repository accompanying this manuscript [ref.].

@@

In this section we give a high-level overview of the \SuperScreen package. Further details can be found in the online documentation~\cite{superscreen-rtd}.

@@

At the time of writing, \SuperScreen requires Python version 3.7--3.9. The package is located in a public repository on GitHub~\cite{superscreen, BishopVanHorn2021-bd}, and a suite of unit tests is run automatically via the GitHub Actions continuous integration (CI) tool whenever a change or proposed change (Pull Request) is made to the \inline{main} branch of the repository. At the time of writing, the test suite is executed using Python versions 3.7 through 3.9, and the test coverage is $>95\%$. Any changes to the \inline{main} branch of the repository also trigger an automatic re-build of the online documentation~\cite{superscreen-rtd}. Stable versions of the package are tagged on GitHub and uploaded to PyPI, the Python Package Index. The source code and documentation are provided under the MIT License.\footnote{\href{https://opensource.org/licenses/MIT}{https://opensource.org/licenses/MIT}}

>>>>

\title{SuperScreen: An open-source package for simulating the magnetic response of two-dimensional superconducting devices}

@@

This introduction to \SuperScreen is organized as follows: In Section~\ref{section:model} we outline the model and its assumptions, and in Section~\ref{section:implementation} we describe its numerical implementation. In Section~\ref{section:overview} we provide an overview of the structure of the \SuperScreen package and discuss some important development details. In Section~\ref{section:examples} we demonstrate how to perform several types of simulations using \SuperScreen and compare the results to analytical solutions and experimental results. Finally, in Section~\ref{section:conlusion} we conclude by discussing applications, limitations, and possible extensions of the package. Python scripts and Jupyter notebooks used to generate all figures presented below can be found in the GitHub repository accompanying this manuscript~\cite{logan_bishop_van_horn_2022_6363541}.

@@

In this section we give a high-level overview of the \SuperScreen package. Further details can be found in the online documentation~\cite{superscreen-rtd}. The specific version of the package corresponding to this manuscript is \texttt{v0.4.0}.

@@

At the time of writing, \SuperScreen requires Python version 3.7--3.9. The package is located in a public repository on GitHub~\cite{superscreen, BishopVanHorn2022-bd}, and a suite of unit tests is run automatically via the GitHub Actions continuous integration (CI) tool whenever a change or proposed change (Pull Request) is made to the \inline{main} branch of the repository. At the time of writing, the test suite is executed using Python versions 3.7 through 3.9, and the test coverage is $>95\%$. Any changes to the \inline{main} branch of the repository also trigger an automatic re-build of the online documentation~\cite{superscreen-rtd}. Stable versions of the package are tagged on GitHub and uploaded to PyPI, the Python Package Index. The source code and documentation are provided under the MIT License.\footnote{\href{https://opensource.org/licenses/MIT}{https://opensource.org/licenses/MIT}}
